### 2010-09-24 paper/IIWAS2010/content/system_arch.tex
latest paper

\section{System Architecure}
\label{sec:systemarch}

@@

We employ a quasi-metric, \textit{class divergence (cd)}, between a source class and a target class using the \textit{topological structure} of the classes in an ontology. We write $S \prec T$ for the reflexive transitive closure of the superclass relation. Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$. The divergence between a source and target class ranges from zero (for identical classes) to one (for type incompatible classes). Let $S$ be the source class, $T$ be the target class, and $C$ be a least common ancestor class of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$. The class divergence between $S$ and $T$ is defined given by:
\begin{equation}
cd(S, T) = \begin{cases}
0 & S.{Uri} \equiv T.{Uri}\\
d(S, T)/(3h) & S \prec T\\
1 & T \prec S\\
(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/(3h) & otherwise
\end{cases}
\end{equation}
where $h$ is the longest path in the ontology class heterarchy.

>>>>

\section{System Architecture}
\label{sec:systemarch}

@@

We define \textit{class divergence} (Eq. \ref{eq:cd}), a quasi-metric, between a source class and a target class using the \textit{topological structure} of the classes in an ontology. We write $S \prec T$ for the reflexive transitive closure of the superclass relation. Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$. The class divergence $cd$, between a source and target class ranges from zero (for identical classes) to one (for type incompatible classes). Let $S$ be the source class, $T$ be the target class, and $C$ be a least common ancestor class of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$. The class divergence between $S$ and $T$ is defined given by:
\begin{equation}
\label{eq:cd}
cd(S, T) = \begin{cases}
0 & S.{Uri} \equiv T.{Uri}\\
d(S, T)/(3h) & S \prec T\\
1 & T \prec S\\
(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/(3h) & otherwise
\end{cases}
\end{equation}
where $h$ is the longest path in the ontology class heterarchy.
